Make any stupid plot you want

### 2021-04-22 draft/sections/next.tex
updated schedule

\subsection{Future Work}
More work is needed to formalize the composition operators, equivalence class \vartisteq, and the mathematical model of interactivity. We also need to implement artists that demonstrate that the model can underpin a minimally viable library, foremost an image\cite{haber1990visualization,hansen2011visualization}, a heatmap\cite{wilkinsonHistoryClusterHeat2009,loua1873atlas}, and an inherently computational artist such as a boxplot\cite{wickham40YearsBoxplots2011}. In summary, the optimistic proposed scope of work is

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|}\hline
    \textbf{work period} & \textbf{milestones \& tasks} \\ \hline
    April-July 2021 & prepare \textbf{conference presentation} on new functionality enabled by model for \textit{SciPy}: artists that do not inherit from existing Matplotlib artists, computational artists such as histograms, non tabular data, composite interactive artist \\ \hline
    June-September 2021  & prepare \textbf{theory paper} on interactivity for submission to \textit{TCVG or Eurovis 2022}: fully work out and describe math of addition operators and lookups from graphic to data space, implement brush linked artist (shared base space) and artist that exploits sheafs \\ \hline
    May - November 2021 & prepare \textbf{applications paper} on high dimensional data for submission to \textit{TCVG}: math and implementation of computational artists, concurrent artists and data sources, non-trivial data bundles \\ \hline 
    August 2020-February 2022 & prepare \textbf{systems paper} on building domain specific libraries based on this model for \textit{Infoviz 2022}: domain specific structured data, composite artists, inference of meta data components, mathematical notion of a visualization (labeled, multiple artists, etc)\\ \hline
    March 2022 & \textbf{dissertation} writing: synthesize previous work on climate data, compile topological equivariant artist model work \\ \hline
    April 2022 & \textbf{defense} \\ \hline
    \end{tabulary}
    \caption{}
    \label{tab:code:schedule}
\end{table}
In acknowledgement that the schedule is optimistic, the data applications of this work could instead be revisited after the defense as that work is not integral to visualization library architecture. The data applications could be further integrated with topological\cite{heineSurveyTopologybasedMethods2016} and functional \cite{ramsayFunctionalDataAnalysis2006a} data analysis methods. Since this model formalizes notions of structure preservation, it can serve as a good base for tools that assess quality metrics\cite{bertiniQualityMetricsHighdimensional2011a} or invariance \cite{kindlmannAlgebraicProcessVisualization2014} of visualizations with respect to graphical encoding choices. While this paper formulates visualization in terms of monoidal action homomorphisms between fiberbundles, the model lends itself to a categorical formulation\cite{fongInvitationAppliedCategory2019,milewskiCategoryTheoryProgrammers} that could be further explored.

>>>>

\subsection{Future Work}
More work is needed to formalize the composition operators, equivalence class \vartisteq, and the mathematical model of interactivity. We also need to implement artists that demonstrate that the model can underpin a minimally viable library, foremost an image\cite{haber1990visualization,hansen2011visualization}, a heatmap\cite{wilkinsonHistoryClusterHeat2009,loua1873atlas}, and an inherently computational artist such as a boxplot\cite{wickham40YearsBoxplots2011}. In summary, the proposed scope of work is

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{2}
    \begin{tabularx}{\textwidth}{|l|X|}\hline
    \textbf{work period} & \textbf{milestones \& tasks} \\ \hline
    April - July 2021  & prepare and submit \textbf{conference presentation} on new functionality enabled by model for \textit{SciPy}: \newline artists that do not inherit from existing Matplotlib artists, computational artists such as histograms, non tabular data, composite interactive artist \\ \hline
    June - Sept 2021  & prepare and submit \textbf{theory paper} on interactivity to \textit{TCVG or Eurovis 2022}: \newline fully work out and describe math of addition operators and lookups from graphic to data space, implement brush linked artist (shared base space) and artist that exploits sheafs \\ \hline
    May - Nov 2021 & prepare and submit \textbf{applications paper} on high dimensional to \textit{TCVG}: \newline math and implementation of computational artists, concurrent artists and data sources, non-trivial data bundles \\ \hline 
    Aug 2021 - Feb 2022 & prepare and submit \textbf{systems paper} on building domain specific libraries based on this model to \textit{Infoviz 2022}: \newline domain specific structured data, composite artists, inference of meta data components, mathematical notion of a visualization (labeled, multiple artists, etc)\\ \hline
    March 2022 & \textbf{dissertation} writing: \newline synthesize previous work on climate data, compile topological equivariant artist model work \\ \hline
    April 2022 & \textbf{defense} \\ \hline
    \end{tabularx}
    \caption{}
    \label{tab:code:schedule}
\end{table}
In acknowledgement that the schedule is optimistic, the data applications of this work could instead be revisited after the defense as that work is not integral to visualization library architecture. The data applications could be further integrated with topological\cite{heineSurveyTopologybasedMethods2016} and functional \cite{ramsayFunctionalDataAnalysis2006a} data analysis methods. Since this model formalizes notions of structure preservation, it can serve as a good base for tools that assess quality metrics\cite{bertiniQualityMetricsHighdimensional2011a} or invariance \cite{kindlmannAlgebraicProcessVisualization2014} of visualizations with respect to graphical encoding choices. While this paper formulates visualization in terms of monoidal action homomorphisms between fiberbundles, the model lends itself to a categorical formulation\cite{fongInvitationAppliedCategory2019,milewskiCategoryTheoryProgrammers} that could be further explored.
